### 2019-04-22 manuscript.rmd
added DAPC and predictions of diet, started updating .bib

  #Compute morphometric ratios
  coiledness = castnumbers$Cnidoband.free.length..um./castnumbers$Cnidoband.length..um.
  heteroneme_elongation = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.width..um.
  haploneme_elongation = castnumbers$Haploneme.free.length..um./castnumbers$Haploneme.width..um.
  desmoneme_elongation = castnumbers$Desmoneme.length..um./castnumbers$Desmoneme.width..um.
  rhopaloneme_elongation = castnumbers$Rhopaloneme.length..um./castnumbers$Rhopaloneme.width..um.
  heteroneme_shaft_extension = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.shaft.free.length..um.
  Heteroneme_to_CB = castnumbers$Heteroneme.free.length..um./(castnumbers$Cnidoband.free.length..um.+0.001)
  total_heteroneme_volume = castnumbers$Heteroneme.volume..um3.*castnumbers$Heteroneme.number
  total_haploneme_volume = (castnumbers$Cnidoband.free.length..um./castnumbers$Haploneme.width..um.)*((4*pi/3)*0.5*castnumbers$Haploneme.free.length..um.*((0.5*castnumbers$Haploneme.width..um.)^2))
  cnidomic_index = log(total_heteroneme_volume + total_haploneme_volume)
  cnidomic_index[which(is.na(cnidomic_index))] <- log(total_haploneme_volume[which(is.na(cnidomic_index))])
  cnidomic_index[which(is.na(cnidomic_index))] <- log(castnumbers[which(is.na(cnidomic_index)), "Heteroneme.volume..um3."])
  cnidomic_index[cnidomic_index==-Inf]<-NA
    morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index)
  names(morphometrics)[1:2] = c("slide_id"," Species")
  castnumbers = data.frame(castnumbers,morphometrics[,c(-1,-2)])

@@

#Make a heatmap
heatdata = as.matrix(castmean_logs[,-1])
rownames(heatdata) = castmean_logs$Species
heatdata[is.nan(heatdata)]<- -1
hcolors = white2blue(19)
hcolors<-c(rep("#000000FF",10), hcolors)
heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)

@@

@@

compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:30)]
#raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))

@@

pGLSp_preylength = as.data.frame(matrix(nrow=ncol(PL_pruned_matrix[,-1]), ncol=1))
colnames(pGLSp_preylength) = "Copepod prey length"
row.names(pGLSp_preylength) = names(PL_pruned_matrix[,-1])
pGLS_PL_sign = pGLSp_preylength
pGLS_sign = pGLSp_preylength
for(i in 2:(ncol(PL_pruned_matrix)-1)){
  CH_I=as.numeric(PL_pruned_matrix[,i])
  names(CH_I) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_J=PL_pruned_matrix[,ncol(PL_pruned_matrix)]
  names(CH_J) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
  SE_I = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),i]
  names(SE_I) = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),1]
  SE_I = SE_I[match(names(CH_I), names(SE_I))]
  pgls_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_I))))
  pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
  pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
  pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
  TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
  TTABLE$`p-value`[2] -> pGLSp_preylength[i-1,1]
  if(pGLSp_preylength[i-1,1]<0.05){
     print(paste(rownames(pGLSp_preylength)[i-1],"Copepod prey length",pGLSp_preylength[(i-1),1],sep=" "))
     ValueIJ = TTABLE %>% .$Value %>% .[2]
     if(ValueIJ>0){pGLS_PL_sign[i-1,1] = "+"}
      else pGLS_PL_sign[i,1] = "-"
  }
}
write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
#pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")
for(i in 2:ncol(PL_pruned_matrix)){
  plot(PL_pruned_matrix[,i], PL_pruned_matrix$`Copepod prey length (mm)`)
}

@@

@@

@@

#Plot mirror trees QUANT
X = dprunedmatrix_logs$Haploneme.free.length..um.
names(X) = dprunedmatrix_logs$Species
X=X[!(is.na(X))]
Y = diet$`Decapod diet`
names(Y) = rownames(diet)

X = nematocyst_number
Y = soft_hard$Soft
Y=softORhard[,1]
names(Y) = rownames(softORhard)
Y[Y!="Soft"]<-0
Y[Y=="Soft"]<-1

Y = Y[which(names(Y) %in% names(X))]
X = X[which(names(X) %in% names(Y))]
treeXY = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(X))))
layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
par(cex=0.5)
#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
OX = contMap(treeXY,X,sig=1,legend=1, plot = F, outline = F)
OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
plot(OX,ftype="off")
ylim<-c(1-0.12*(length(treeXY$tip.label)-1),length(treeXY$tip.label))
plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
text(rep(0,length(treeXY$tip.label)), 1:length(treeXY$tip.label),treeXY$tip.label)
OY = contMap(treeXY,Y, sig=1,legend=1, plot = F,  outline = F)
OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
plot(OY, direction="leftwards", ftype = "off")

X = Pprunedmatrix_logs$Heteroneme.volume..um3.
names(X) = Pprunedmatrix_logs$Species
Y = PP$`Relative decapod consumption`
names(Y) = rownames(PP)
layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
par(cex=0.5)
#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
OX = contMap(Pprunedtree,X,sig=1,legend=1, plot = F, outline = F)
OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
plot(OX,ftype="off")
ylim<-c(1-0.12*(length(Pprunedtree$tip.label)-1),length(Pprunedtree$tip.label))
plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
text(rep(0,length(Pprunedtree$tip.label)), 1:length(Pprunedtree$tip.label),Pprunedtree$tip.label)
OY = contMap(Pprunedtree,Y, sig=1,legend=1, plot = F,  outline = F)
OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
plot(OY, direction="leftwards", ftype = "off")

@@

#Using compound mosphospace
# compcoords = Pca_compound$ind$coord[,1:2]
# compcoords = compcoords[which(rownames(compcoords) %in% names(hypdiet)),]
# OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
# names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
# library(magrittr)
# for(c in 1:ncol(compcoords)){
#   Cdata = data.frame(rownames(compcoords),hypdiet[which(names(hypdiet) %in% rownames(compcoords))],compcoords[,c])
#   names(Cdata) = c("species", "regime", "trait")
#   Cdata$trait[which(Cdata$trait == "NaN")] <- NA
#   Cdata = Cdata[!is.na(Cdata$trait),]
#   Cdata$trait = as.numeric(Cdata$trait)
#   Cdata$species = as.character(Cdata$species)
#   Cdata$regime = as.character(Cdata$regime)
#   Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
#   BM <- OUwie(Ctree, Cdata, model="BM1")
#   OU1 <- OUwie(Ctree, Cdata, model="OU1")
#   OUm <- OUwie(Ctree, Cdata, model="OUMV")
#   OUwie_matrix[c,1] = c("PC1","PC2")[c]
#   OUwie_matrix[c,2] = nrow(Cdata)
#   OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
#   OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
#   OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
# }
# OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
# write.csv(OUwie_matrix, "OU_compound_test.csv")
```

>>>>

  #Compute morphometric ratios
  coiledness = castnumbers$Cnidoband.free.length..um./castnumbers$Cnidoband.length..um.
  heteroneme_elongation = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.width..um.
  haploneme_elongation = castnumbers$Haploneme.free.length..um./castnumbers$Haploneme.width..um.
  desmoneme_elongation = castnumbers$Desmoneme.length..um./castnumbers$Desmoneme.width..um.
  rhopaloneme_elongation = castnumbers$Rhopaloneme.length..um./castnumbers$Rhopaloneme.width..um.
  heteroneme_shaft_extension = castnumbers$Heteroneme.free.length..um./castnumbers$Heteroneme.shaft.free.length..um.
  Heteroneme_to_CB = castnumbers$Heteroneme.free.length..um./(castnumbers$Cnidoband.free.length..um.+0.001)
  total_heteroneme_volume = castnumbers$Heteroneme.volume..um3.*castnumbers$Heteroneme.number
  total_haploneme_volume = (castnumbers$Cnidoband.free.length..um./castnumbers$Haploneme.width..um.)*((4*pi/3)*0.5*castnumbers$Haploneme.free.length..um.*((0.5*castnumbers$Haploneme.width..um.)^2))
  cnidomic_index = log(total_heteroneme_volume + total_haploneme_volume)
  cnidomic_index[which(is.na(cnidomic_index))] <- log(total_haploneme_volume[which(is.na(cnidomic_index))])
  cnidomic_index[which(is.na(cnidomic_index))] <- log(castnumbers[which(is.na(cnidomic_index)), "Heteroneme.volume..um3."])
  cnidomic_index[cnidomic_index==-Inf]<-NA
  surface_ellipsoid <- function(L, W){
  a <- L/2
  b <- W/2
  c = b
  S <- 4*pi*((((a*b)^1.6)+((a*c)^1.6)+((c*b)^1.6))/3)^(1/1.6)
  return(S)
}
volume_ellipsoid <- function(L, W){
  a <- L/2
  b <- W/2
  c = b
  V <- (4/3)*pi*a*b*c
  return(V)
}
SAV_haploneme = surface_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)/volume_ellipsoid(castnumbers$Haploneme.free.length..um., castnumbers$Haploneme.width..um.)
names(SAV_haploneme) = castnumbers$Species
SAV_heteroneme = surface_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)/volume_ellipsoid(castnumbers$Heteroneme.free.length..um., castnumbers$Heteroneme.width..um.)
names(SAV_heteroneme) = sharedmeans$Species
morphometrics = data.frame(castnumbers$slide_id, castnumbers$Species,coiledness, heteroneme_elongation, haploneme_elongation, desmoneme_elongation, rhopaloneme_elongation,heteroneme_shaft_extension, Heteroneme_to_CB, total_heteroneme_volume, total_haploneme_volume, cnidomic_index, SAV_haploneme)
  names(morphometrics)[1:2] = c("slide_id"," Species")
  castnumbers = data.frame(castnumbers,morphometrics[,c(-1,-2)])

@@

#Make a heatmap
heatdata = as.matrix(castmean_logs[,-1])
rownames(heatdata) = castmean_logs$Species
heatdata[is.nan(heatdata)]<- -1
hcolors = grDevices::terrain.colors(20)
hcolors<-c(rep("#000000FF",10), hcolors)
heatmap(heatdata, scale = "column", cexCol = 0.2, col=hcolors, keep.dendro = T)

@@

#SURFACE AREA : VOLUME
SAV_haploneme = surface_ellipsoid(sharedmeans$Haploneme.free.length..um., sharedmeans$Haploneme.width..um.)/volume_ellipsoid(sharedmeans$Haploneme.free.length..um., sharedmeans$Haploneme.width..um.)
names(SAV_haploneme) = sharedmeans$Species
SAV_heteroneme = surface_ellipsoid(sharedmeans$Heteroneme.free.length..um., sharedmeans$Heteroneme.width..um.)/volume_ellipsoid(sharedmeans$Heteroneme.free.length..um., sharedmeans$Heteroneme.width..um.)
names(SAV_heteroneme) = sharedmeans$Species
SAV_haploneme = SAV_haploneme[which(!is.nan(SAV_haploneme))]
SAV_heteroneme = SAV_heteroneme[which(!is.nan(SAV_heteroneme))]
SAVhet_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(SAV_heteroneme))))
Phenogram(SAV_heteroneme, as.data.frame(SAV_heteroneme), SAVhet_tree)
Phenogram(SAV_haploneme, as.data.frame(SAV_haploneme), hap_tree)

@@

compound_matrix = Q_sharedmean_logs[which(!is.na(rowSums(Q_sharedmean_logs))),c(3,21:31)]
#raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix))))
raw_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(raw_matrix_notf))))
compound_tree = drop.tip(ultram, which(!(ultram$tip.label %in% rownames(compound_matrix))))

@@

pGLSp_preylength = as.data.frame(matrix(nrow=ncol(PL_pruned_matrix[,-1]), ncol=1))
colnames(pGLSp_preylength) = "Copepod prey length"
row.names(pGLSp_preylength) = names(PL_pruned_matrix[,-1])
pGLS_PL_sign = pGLSp_preylength
pGLS_sign = pGLSp_preylength
for(i in 2:(ncol(PL_pruned_matrix)-1)){
  CH_I=as.numeric(PL_pruned_matrix[,i])
  names(CH_I) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_J=PL_pruned_matrix[,ncol(PL_pruned_matrix)]
  names(CH_J) = PL_pruned_matrix$Species
  CH_I = CH_I[!is.na(CH_I)]
  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
  SE_I = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),i]
  names(SE_I) = PL_pruned_SEs[which(PL_pruned_SEs$Species %in% names(CH_I)),1]
  SE_I = SE_I[match(names(CH_I), names(SE_I))]
  pgls_tree = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_I))))
  pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
  pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
  pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
  TTABLE <- gls(CH_I ~ CH_J, correlation =  corBrownian(phy = pgls_tree), data = pg_data, method = "ML") %>% summary() %>% .$tTable %>% as.data.frame()
  TTABLE$`p-value`[2] -> pGLSp_preylength[i-1,1]
  if(pGLSp_preylength[i-1,1]<0.05){
     print(paste(rownames(pGLSp_preylength)[i-1],"Copepod prey length",pGLSp_preylength[(i-1),1],sep=" "))
     ValueIJ = TTABLE %>% .$Value %>% .[2]
     if(ValueIJ>0){pGLS_PL_sign[i-1,1] = "+"}
      else pGLS_PL_sign[i,1] = "-"
  }
}
#write.csv(pGLSp_preylength, "PGLS_Pval_preylength.csv")
#pGLS_PL_sign <- pGLS_PL_sign[which(rowSums(is.na(pGLS_PL_sign))!=ncol(pGLS_PL_sign)),which(colSums(is.na(pGLS_PL_sign))!=nrow(pGLS_PL_sign))]
write.csv(pGLS_PL_sign, "PGLS_SIGN_preylength.csv")
for(i in 2:ncol(PL_pruned_matrix)){
  plot(PL_pruned_matrix[,i], PL_pruned_matrix$`Copepod prey length (mm)`)
}

@@

#SA/V Haplonemes
CH_J=softORhard[,1]
names(CH_J) = rownames(softORhard)
CH_J[CH_J!="Soft"]<-0
CH_J[CH_J=="Soft"]<-1
CH_I = SAV_haploneme
CH_J = CH_J[which(names(CH_J)%in%names(CH_I))]
CH_I = CH_I[which(names(CH_I)%in%names(CH_J))]
treeIJ = drop.tip(ultram, which(!(ultram$tip.label %in% names(CH_J))))
CH_I = CH_I[match(treeIJ$tip.label, names(CH_I))]
CH_J = CH_J[match(treeIJ$tip.label, names(CH_J))]
datIJ = data.frame(preytype = CH_J, character = CH_I)
datIJ$preytype = as.numeric(as.character(datIJ$preytype))
logit = glm(preytype~character,data=datIJ, family="binomial")
    print(logit)
phylogit = phyloglm(preytype~character,phy=treeIJ,data=datIJ,boot=10, btol=10)
    print(phylogit)
c("Soft specilization", "Haploneme SA:V", phylogit$n, phylogit$aic, coef(summary(phylogit))[2,6], coef(summary(phylogit))[2,1], logit$aic, coef(summary(logit))[2,4], coef(summary(logit))[2,1])
```

@@

#Haploneme SA/V to diet
CH_I=SAV_haploneme
CH_I = CH_I[!is.na(CH_I)]
for(j in 1:ncol(selectivity)){
  CH_J=as.numeric(selectivity[,j])
  names(CH_J) = rownames(selectivity)
  CH_J = CH_J[!is.na(CH_J)]
  CH_I = CH_I[which(names(CH_I) %in% names(CH_J))]
  CH_J = CH_J[which(names(CH_J) %in% names(CH_I))]
  SE_I = castSE_logs[which(castSE$Species %in% names(CH_I)),i]
    names(SE_I) = castSE_logs[which(castSE$Species %in% names(CH_I)),1]
    SE_I = SE_I[match(names(CH_I), names(SE_I))]
    pgls_tree = drop.tip(Sprunedtree, which(!(Sprunedtree$tip.label %in% names(CH_I))))
    pg_data = as.data.frame(cbind(CH_I,CH_J)) %>% .[which(!is.na(rowSums(.))),]
    if(length(unique(CH_J))>1){
          pgls.SEy(CH_I~CH_J, data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE
          pgls.SEy(CH_I~sample(CH_J, length(CH_J)), data=pg_data, tree = pgls_tree, se = SE_I) -> TTABLE_null
          LikRat <- 2*(TTABLE$logLik[1] - TTABLE_null$logLik[1])
          pchisq(LikRat, df=1, lower.tail = F) -> pGLSp_sel[i-1,j]
          if(pGLSp_sel[i-1,j]<0.05){
          print(paste(rownames(pGLSp_sel)[i-1],colnames(pGLSp_sel)[j],pGLSp_sel[(i-1),(j)],TTABLE$coefficients[2], sep=" "))
          ValueIJ = TTABLE %>% .$coefficients %>% .[2]
          if(ValueIJ>0){pGLS_sel_sign[i-1,j] = "+"}
          else pGLS_sel_sign[i,j] = "-"
         }
       }
    else TTABLE<-NA; TTABLE_null<-NA; LikRat<-NA; pGLSp_sel[i-1,j]<-NA
  }

@@

#Plot mirror trees QUANT
X = dprunedmatrix_logs$Haploneme.row.number
names(X) = dprunedmatrix_logs$Species
X=X[!(is.na(X))]
Y = diet$`Decapod diet`
names(Y) = rownames(diet)

X = dprunedmatrix_logs$coiledness
names(X) = dprunedmatrix_logs$Species
X<-X[!(is.nan(X))]
Y = diet$`Decapod diet`
#Y=softORhard[,1]
names(Y) = rownames(diet)
#Y[Y!="Soft"]<-0
#Y[Y=="Soft"]<-1
Y = Y[which(names(Y) %in% names(X))]
X = X[which(names(X) %in% names(Y))]
treeXY = drop.tip(dprunedTree, which(!(dprunedTree$tip.label %in% names(X))))
layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
par(cex=0.5)
#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
OX = contMap(treeXY,X,sig=1,legend=1, plot = F, outline = F)
OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
plot(OX,ftype="off")
ylim<-c(1-0.12*(length(treeXY$tip.label)-1),length(treeXY$tip.label))
plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
text(rep(0,length(treeXY$tip.label)), 1:length(treeXY$tip.label),treeXY$tip.label)
OY = contMap(treeXY,Y, sig=1,legend=1, plot = F,  outline = F)
OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
plot(OY, direction="leftwards", ftype = "off")

X = Sprunedmatrix_logs$Haploneme.row.number..um.
names(X) = Sprunedmatrix_logs$Species
Y = selectivity$Selectivity.Decapod.larvae #PP$`Relative decapod consumption`
names(Y) = rownames(selectivity)
layout(matrix(1:3,1,3),widths=c(0.44,0.12,0.44))
par(cex=0.5)
#pdf("deliverables/Hvol_copepod.pdf",width=10,height=6)
OX = contMap(Sprunedtree,X,sig=1,legend=1, plot = F, outline = F)
OX$cols[1:length(OX$cols)] = colorRampPalette(c("blue","red"), space="Lab")(length(OX$cols))
plot(OX,ftype="off")
ylim<-c(1-0.12*(length(Sprunedtree$tip.label)-1),length(Sprunedtree$tip.label))
plot.new(); plot.window(xlim=c(-0.1,0.1),ylim=ylim)
text(rep(0,length(Sprunedtree$tip.label)), 1:length(Sprunedtree$tip.label),Sprunedtree$tip.label)
OY = contMap(Sprunedtree,Y, sig=1,legend=1, plot = F,  outline = F)
OY$cols[1:length(OY$cols)] = colorRampPalette(c("orange","green"), space="Lab")(length(OY$cols))
plot(OY, direction="leftwards", ftype = "off")

@@

#Using compound mosphospace
# compcoords = Pca_compound$ind$coord[,1:2]
# compcoords = compcoords[which(rownames(compcoords) %in% names(hypdiet)),]
# OUwie_matrix = as.data.frame(matrix(ncol=4, nrow=2))
# names(OUwie_matrix) = c("Character", "Ntips", "dAICc_BM", "dAICc_OU1", "dAICc_OUMV")
# library(magrittr)
# for(c in 1:ncol(compcoords)){
#   Cdata = data.frame(rownames(compcoords),hypdiet[which(names(hypdiet) %in% rownames(compcoords))],compcoords[,c])
#   names(Cdata) = c("species", "regime", "trait")
#   Cdata$trait[which(Cdata$trait == "NaN")] <- NA
#   Cdata = Cdata[!is.na(Cdata$trait),]
#   Cdata$trait = as.numeric(Cdata$trait)
#   Cdata$species = as.character(Cdata$species)
#   Cdata$regime = as.character(Cdata$regime)
#   Ctree = drop.tip(regimetree,which(!(regimetree$tip.label %in% Cdata$species)))
#   BM <- OUwie(Ctree, Cdata, model="BM1")
#   OU1 <- OUwie(Ctree, Cdata, model="OU1")
#   OUm <- OUwie(Ctree, Cdata, model="OUMV")
#   OUwie_matrix[c,1] = c("PC1","PC2")[c]
#   OUwie_matrix[c,2] = nrow(Cdata)
#   OUwie_matrix[c,3] = BM$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
#   OUwie_matrix[c,4] = OU1$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
#   OUwie_matrix[c,5] = OUm$AICc - min(c(BM$AICc, OU1$AICc, OUm$AICc))
# }
# OUwie_matrix[,3:5] <- apply(OUwie_matrix[,3:5], 2, round3)
# write.csv(OUwie_matrix, "OU_compound_test.csv")

#DAPC diet??
library(adegenet)
rowNAs = c(0,apply(sharedmean_logs[,-1], 1, function(x) sum(is.nan(x))))
colNAs = c(0,apply(sharedmean_logs[,-1], 2, function(x) sum(is.nan(x))))
ldamtrix = sharedmean_logs[,which(colNAs<6)]
#ldamtrix = sharedmean_logs[which(rowNAs<20),]
ldamtrix = ldamtrix[which(!is.nan(rowSums(ldamtrix[,-1]))),]
#ldamtrix = ldamtrix[,which(!is.nan(colSums(ldamtrix[,-1])))]
#rowNAs = apply(ldamtrix[,-1], 1, function(x) sum(is.na(x)))
#colNAs = apply(ldamtrix[,-1], 2, function(x) sum(is.nan(x)))
ldamtrix = ldamtrix[which(rowNAs<1),]
#ldamtrix = ldamtrix[,which(colNAs<1)]
ldamtrix$Species = as.character(ldamtrix$Species)
ldamtrix = ldamtrix[which(ldamtrix$Species %in% names(hypdiet)),]
#ldamtrix = ldamtrix[which(ldamtrix$Species %in% rownames(diet)),]
LDAtree = drop.tip(ultram, which(!(ultram$tip.label %in% ldamtrix$Species)))
ldamtrix = ldamtrix[match(LDAtree$tip.label, ldamtrix$Species),]
baselda=ldamtrix

#Feeding guild
prunediets = hypdiet[which(names(hypdiet) %in% ldamtrix$Species)]
ldamtrix = cbind(baselda, prunediets[match(baselda$Species, names(prunediets))])
names(ldamtrix)[ncol(ldamtrix)]<-"Diet"
#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$Diet, n.pca.max = 300, training.set = 0.9,
                 result = "groupMean", center = TRUE, scale = TRUE,
                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$Diet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
scatter(DAPClogs, clabel = 0.5)
assignplot(DAPClogs)
compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")

prunediets = diet[which(rownames(diet) %in% ldamtrix$Species),]
#Copepods
ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), "Copepod diet"])
names(ldamtrix)[ncol(ldamtrix)]<-"CopepodDiet"
#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$CopepodDiet, n.pca.max = 300, training.set = 0.9,
                 result = "groupMean", center = TRUE, scale = TRUE,
                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$CopepodDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
summary.dapc(DAPClogs)
contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
scatter(DAPClogs, clabel = 0.5)
assignplot(DAPClogs)
compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
copselmatrix = cbind(Sprunedmatrix, selectivity$Selectivity.Copepods)
copselmatrix = copselmatrix[which(copselmatrix$Species %in% LDAtree$tip.label),]
copselmatrix = copselmatrix[match(LDAtree$tip.label, copselmatrix$Species),]
CopepodGLM <- glm(CopepodDiet~Tentacle.width..um.+Haploneme.row.number..um., data = ldamtrix)
summary(CopepodGLM)
1-(CopepodGLM$deviance/CopepodGLM$null.deviance) #76.2
CopepodSelGLM <- glm(selectivity$Selectivity.Copepods~Tentacle.width..um.+Haploneme.row.number..um.+total_haploneme_volume, data = copselmatrix)
summary(CopepodSelGLM)
1-(CopepodSelGLM$deviance/CopepodSelGLM$null.deviance) #76.6%
rownames(ldamtrix) = ldamtrix$Species
CopepodPGLM <- phyloglm(CopepodDiet~Tentacle.width..um.+Haploneme.row.number..um., data = ldamtrix, phy = LDAtree, btol=100)
summary(CopepodPGLM)
predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
predictionset[is.na(predictionset)]<-0
rownames(predictionset)<-predictionset$Species
predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
preDIET <- predict(DAPClogs, predictionset[,-1])
cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)

#Fish
ldamtrix = cbind(baselda, prunediets[match(baselda$Species, rownames(prunediets)), "Fish diet"])
names(ldamtrix)[ncol(ldamtrix)]<-"FishDiet"
#ldamtrix[,c(-1,-ncol(ldamtrix))] <- apply(ldamtrix[,c(-1,-ncol(ldamtrix))],2,exp)
xval <- xvalDapc(ldamtrix[,c(-1,-ncol(ldamtrix))], ldamtrix$FishDiet, n.pca.max = 300, training.set = 0.9,
                 result = "groupMean", center = TRUE, scale = TRUE,
                 n.pca = NULL, n.rep = 30, xval.plot = TRUE)
dapc(ldamtrix[,c(-1,-ncol(ldamtrix))], grp=ldamtrix$FishDiet, n.pca = xval$DAPC$n.pca, n.da = xval$DAPC$n.da) -> DAPClogs
summary.dapc(DAPClogs)
contrib <- loadingplot(DAPClogs$var.contr, axis=1, lab.jitter=1)
scatter(DAPClogs, clabel = 0.5)
assignplot(DAPClogs)
compoplot(DAPClogs, posi="bottomright", lab="",ncol=1, xlab="individuals", cex.leg = 0.1, col.pal = "funky")
FishGLM <- glm(FishDiet~Heteroneme.volume..um3.+total_haploneme_volume+Pedicle.width..um., data = ldamtrix)
summary(FishGLM)
1-(FishGLM$deviance/FishGLM$null.deviance)
fishselmatrix = cbind(Sprunedmatrix, selectivity$Selectivity.Fish)
fishselmatrix = fishselmatrix[which(fishselmatrix$Species %in% ldamtrix$Species),]
fishselmatrix = fishselmatrix[match(LDAtree$tip.label, fishselmatrix$Species),]
FishSelGLM <- glm(selectivity$Selectivity.Fish~Pedicle.width..um., data = fishselmatrix)
summary(FishSelGLM)
1-(FishSelGLM$deviance/FishSelGLM$null.deviance) #97.5%
predictionset <- castmean_logs[,which(names(castmean_logs) %in% names(ldamtrix))]
predictionset[is.na(predictionset)]<-0
rownames(predictionset)<-predictionset$Species
predictionset=predictionset[which(!(predictionset$Species %in% c("Thermopalia taraxaca", "Nectadamas richardi", "Halistemma cupulifera", "Cardianecta parchelion"))),]
predictionset=predictionset[which(!(predictionset$Species %in% ldamtrix$Species)),]
preDIET <- predict(DAPClogs, predictionset[,-1])
cbind(predictionset$Species, as.character(preDIET$assign)) %>% View()
preDIET$posterior %>% round(5) %>%  as.matrix() %>% heatmap(scale="row", cexCol=0.5, col=c("white","white",gray.colors(10)[10:1],"black"),Colv=NA)
